### 2017-07-04 readme.Rmd
readme update

```{r,warning=FALSE,error=FALSE,message=FALSE}
library(mgcv)
bkpts_quasi <- generate_background_points(number_of_background_points = 20000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')
fm_warton2010 <- gam(presence/weights ~ s(elevation) +
              s(precipitation) +
              s(temperature) +
              s(vegetation),
              weights = weights,
              data = bkpts_quasi,
              family = poisson())

p_warton <- predict(object=preds,
             model=fm_warton2010,
             type = 'response',
             const=data.frame(weights = 1))

p_warton_cell <- p_warton*(res(preds)[1]*res(preds)[2])/4 # resolution of raster changes with bkpts_quasi - need to remember that.

@@

Now let's plot these models.
```{r,fig.width=8,fig.height=6}
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_warton_cell,col=jet.colors(100))
```

@@

```{r}
raster::cellStats(p_warton_cell,sum)
nrow(sp_sites)
```

>>>>

```{r,warning=FALSE,error=FALSE,message=FALSE}
library(mgcv)
bkpts_quasi <- generate_background_points(number_of_background_points = 20000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')
fm <- gam(presence/weights ~ s(elevation) +
              s(precipitation) +
              s(temperature) +
              s(vegetation),
              weights = weights,
              data = bkpts_quasi,
              family = poisson())

p <- predict(object=preds,
             model=fm,
             type = 'response',
             const=data.frame(weights = 1))

p_cell <- p*(res(preds)[1]*res(preds)[2])/4 # resolution of raster changes with bkpts_quasi - need to remember that.

@@

Now let's plot these models.
```{r,fig.width=8,fig.height=6}
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_cell,col=jet.colors(100))
```

@@

```{r}
raster::cellStats(p_cell,sum)
nrow(sp_sites)
```
